`r params$doc_title`

### 2022-11-14 scripts/MSc.Rmd
slight changes before nightshift

    # PERFORM MR_analysis
    mr.obj = MendelianRandomization::mr_input(
          bx = sim_dat$beta.bmi_sim_norm, 
          bxse = sim_dat$se_update_BMI, 
          # outcome
          by = sim_dat$beta.gbc_sim_norm, 
          byse = sim_dat$se_update_GBC, 
          snps = sim_dat$SNP,
          exposure = "Body mass index",
          outcome = "Gallbladder Cancer"
        ) 
    # CONMIX (as reference)
    res = MendelianRandomization::mr_conmix(mr.obj)
    colname_theta <- paste0("theta_sim_", n[i])
    colname_theta_se <- paste0("theta_se_sim_", n[i])
    ## store results
    est[k, colname_theta] <- res$Estimate
    CIlength = res$CIUpper-res$CILower
    if (length(CIlength)>1) print("conmix multimodal")
    est[k, colname_theta_se] <- sum(CIlength)/1.96/2  ## Caution: this may be problematic 
    rm(res)
  }
  print(paste0("|||-----------------------Run finished for sample size: ", n[i], " -----------------------|||"))
}
T1 = proc.time()[3]
timediff = T1-T0
```

>>>>

    # PERFORM MR_analysis
    mr.obj = MendelianRandomization::mr_input(
          bx = sim_dat$beta.bmi_sim_norm, 
          bxse = sim_dat$se_update_BMI, 
          # outcome
          by = sim_dat$beta.gbc_sim_norm, 
          byse = sim_dat$se_update_GBC, 
          snps = sim_dat$SNP,
          exposure = "Body mass index",
          outcome = "Gallbladder Cancer"
        ) 
    # CONMIX (as reference)
    res = MendelianRandomization::mr_conmix(mr.obj)
    colname_theta <- paste0("theta_sim_", n[i])
    colname_theta_se <- paste0("theta_se_sim_", n[i])
    ## store results
    est[k, colname_theta] <- res$Estimate
    CIlength = res$CIUpper-res$CILower
    if (length(CIlength)>1) print("conmix multimodal")
    est[k, colname_theta_se] <- sum(CIlength)/1.96/2  ## Caution: this may be problematic 
    rm(res)
  }
  print(paste0("|||-----------------------Run finished for sample size: ", n[i], " -----------------------|||"))
}
T1 = proc.time()[3]
timediff = T1-T0

saveRDS(est, paste0(Sys.Date(), "_est.rds")
